---
title: "Assignment_3"
author: "Khutso Ledwaba"
date: "2022-10-13"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

*Calling the data file and the required packages*
```{r}
library("ggplot2")
library("gmodels")
library("caret")
library("ISLR")
library("class")
library("e1071")
library("dplyr")
library("melt")
library("reshape")
library("reshape2")
library("readr")
library("ISLR")
library("pROC")
UBData <- read.csv("UniversalBank.csv")
UBData <- data.frame(read.csv("UniversalBank.csv"))
UBData

str(UBData)
```

*Partitioning the data into Training_Dataing and validation sets*
```{r}
#Converting the predictor attributes to factors
UBData$CreditCard <- as.factor(UBData$CreditCard)
UBData$Personal.Loan <- as.factor(UBData$Personal.Loan)
UBData$Online <- as.factor(UBData$Online)


test.na <- is.na.data.frame(UBData)


set.seed(678)
Partition_data <- createDataPartition(UBData$Personal.Loan,p=.6, list=F)
Training_Data <- UBData[Partition_data,]
Validate_Data <- UBData[-Partition_data,]

#Data Normalization
norm_model <- preProcess(Training_Data[,-c(10,13:14)], 
                method=c("center","scale"))
Training_Data_norm <- predict(norm_model,Training_Data)
Validate_Data_norm <- predict(norm_model,Validate_Data)
```

## Question A 
```{r}
table_1 <- ftable(Training_Data_norm[,c(14,10,13)])
table_1
```

##Question B
$$
\text{ The probability of a customer accepting a loan offer while being an active online banking user is  = 51/(51+467) = 0.0984}
$$


## Question C
```{r}
Online <- melt(Training_Data_norm,id=c("Personal.Loan"),variable="Online")
Creditcard <- melt(Training_Data_norm,id=c("Personal.Loan"), variable="CreditCard")
cast_online <- dcast(Online, Personal.Loan~Online)
cast_creditcard <- dcast(Creditcard, Personal.Loan~CreditCard)
```

## Question D
```{r}
ftable(Training_Data_norm[,c(10,13)])
ftable(Training_Data_norm[,c(10,14)])
ftable(Training_Data_norm[,10])
```


*1. P(CreditCard = 1 | Personal.Loan = 1) = 84/(84+204) =* ***0.2916***\vspace{3mm}\newline
*2. P(Online= 1 | Personal.Loan= 1) = 176/(176+112) =* ***0.6111***\vspace{3mm} \newline
*3. P(Personal.Loan = 1) = 288/(288+2712) =* ***0.096***\vspace{3mm} \newline
*4. P(CreditCard= 1 | Personal.Loan= 0) = 777/(777+1935) =* ***0.2865***\vspace{3mm} \newline
*5. P(Online=1 |Personal.Loan=0) = 1611/(1611+1101) =* ***0.5940***\vspace{3mm} \newline
*6. P(Personal.Loan = 0) = 2712/(2712+288) =* ***0.904***\vspace{3mm} \newline




## Question E
$$

(0.2916 x0.6111 x 0.096) / (0.2916 x 0.6111 x 0.096) + (0.2865 x 0.5940 x 0.904) = 0.1000\\
$$

##Question F
$$

\text {By comparing the value obtained above by using the Naive Bayes probability i.e. 0.1000 to the value obtained in step b i.e. 0.0984 we get to see that both the values are almost similar, but Naive Bayes has a bit higher probability when compared to that with the direct calculation}

$$
## Question G
```{r}
NB <- naiveBayes(Personal.Loan~Online+CreditCard,data=Training_Data_norm)
NB
```

$$
\text {The value obtained when I ran the Naive Bayes Model for the customer is equivalent to the value obtained in E}
$$

