---
title: "Assignment_2"
author: "Khutso Ledwaba"
date: "2022-10-05"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Call the data file
```{r}
UBData <- data.frame(read.csv("UniversalBank.csv"))
UBData

str(UBData)
library("ggplot2")
library("gmodels")
library("caret")
library("ISLR")
library("class")
```
##Organizing UB data
```{r}
UBData <- UBData[,c(-1,-5)]
head(UBData, n=7)
tail(UBData, n=7)

##Converting Personal loan and Education to factors
UBData$Education <- as.factor(UBData$Education)

UBData$Personal.Loan <- as.factor(UBData$Personal.Loan)

##creating Dummy variables for Education
UBData_Dummy <- dummyVars(~Education, UBData)
head(predict(UBData_Dummy, UBData))

UB2 <- predict(UBData_Dummy,UBData)

UB3 <- UBData[,-10]
UB <- cbind(UB3,UB2)
colnames(UB)
```
##Set the seed function as 14
```{r}
set.seed(14)
```

##Training and Validation sets 
```{r}
UBData_Train <- createDataPartition(UB$Personal.Loan, p=0.6, list=F)
#Training data
UB_Training <- UB[UBData_Train,]
#Validation data
UB_Validation <- UB[-UBData_Train,]

#Normalizing the training and validation data

Normalized.values <- preProcess(UB_Training[, -c(8)], method=c("center", "scale"))
UB_TrainingNormalized <- predict(Normalized.values, UB_Training[, -c(8)])
UB_ValidationNormalized <- predict(Normalized.values, UB_Validation[, -c(8)])


```


##Normalizing the customer data set
```{r}
CustomerData <- cbind.data.frame(Age = 40,Experience = 10, Income = 84, Family = 2, CCAvg = 2, Mortgage = 0, Securities.Account = 0, CD.Account = 0, Online = 1, CreditCard = 1, Education1 = 0, Education2 = 1, Education3 = 0)

CustomerData
#Normalizing the data
UB_TestNorm<- predict(Normalized.values, CustomerData)
```

#Question 1
```{r}

K.Value <- knn(Train=UB_TrainingNormalized[, -c(8)], Test = UB_TestNorm , cl=UB_TrainingNormalized[, -c(8)], k=1)

knn.attributes <- attributes(K.Value)

knn.attributes[1]

head(K.Value)
```
The loan was not accepted as when K=1 the customer value is 0 and 0 is defined as the loan being denied.


# Question number 2
```{r}
set.seed(800)
search_grid <- expand.grid(k=c(1:30))

Example <- train(Personal.Loan~Age+Experience+Income+Family+CCAvg+Mortgage+Securities.Account+CD.Account+Online+CreditCard+Education1+Education2+Education3, data=UB_TrainingNormalized, method="knn", Grid = search_grid)
Example
K <- Example$bestTune[[1]]
K
```
The best value is where k = 1. 

# Question 3
```{r}
CF <- predict(Example,UB_ValidationNormalized[,(-8)])

confusionMatrix(CF, UB_ValidationNormalized[8])
```


# Question 4
```{r}
CustomerData2= data.frame(Age = 40, Experience = 10, Income = 84, Family = 2, CCAvg = 2, Education_1 = 0, Education_2 = 1, Education_3 = 0, Mortgage = 0, Securities.Account = 0, CD.Account = 0, Online = 1, CreditCard = 1, stringAsFactors = FALSE)

K.Value2 <- knn(train = UB_TrainingNormalized[,(-8)],test = CustomerData2, cl = UB_TrainingNormalized[,(8)], k=k)
K.Value2
```
The customer is listed as 0 and shows that the loan has been denied

#question 5
set.seed(800)